---
title: "model_predictions"
output: html_document
---

```{r setup}
library(sf)
library(tidyverse)
library(sdmTMB)
library(geoR)
```

# Read and manipulate data
### Read in datasets

```{r read in data}
# Read in SFES data
SFES <- readRDS("../Input_data/SFES_clean_080222.rds")
```

# Generate predictions on original data points

### Striped Bass

```{r}
# Read in striped bass model
mSTRBAS <- read_rds("../output_models/042022/mSTRBAS.rds")

# Generate prediction on original data points
pSTRBAS_SFES <- predict(mSTRBAS, newdata = SFES, return_tmb_object = TRUE)

# Save prediction
saveRDS(pSTRBAS_SFES, "../predictions/042022/pSTRBAS_SFES.rds")
```

### Delta Smelt

```{r}
# Read in Delta Smelt model
mDELSME <- read_rds("../output_models/042022/mDELSME.rds")

# Generate prediction on original data points
pDELSME_SFES <- predict(mDELSME, newdata = SFES, return_tmb_object = TRUE)

# Save prediction
saveRDS(pDELSME_SFES, "../predictions/042022/pDELSME_SFES.rds")
```

### Longfin Smelt

```{r}
# Read in Longfin Smelt model
mLONSME <- read_rds("../output_models/042022/mLONSME.rds")

# Generate prediction on original data points
pLONSME_SFES <- predict(mLONSME, newdata = SFES, return_tmb_object = TRUE)

# Save prediction
saveRDS(pLONSME_SFES, "../predictions/042022/pLONSME_SFES.rds")
```

### Threadfin Shad

```{r}
# Read in Threadfin Shad model
mTHRSHA <- read_rds("../output_models/042022/mTHRSHA.rds")

# Generate prediction on original data points
pTHRSHA_SFES <- predict(mTHRSHA, newdata = SFES, return_tmb_object = TRUE)

# Save prediction
saveRDS(pTHRSHA_SFES, "../predictions/042022/pTHRSHA_SFES.rds")
```

### American Shad

```{r}
# Read in American Shad model
mAMESHA <- read_rds("../output_models/042022/mAMESHA.rds")

# Generate prediction on original data points
pAMESHA_SFES <- predict(mAMESHA, newdata = SFES, return_tmb_object = TRUE)

# Save prediction
saveRDS(pAMESHA_SFES, "../predictions/042022/pAMESHA_SFES.rds")
```

# Read in and modify prediction grid for predicting estuary wide distributions

```{r}
# Read in slimmed prediction grid
SFE_grid <- readRDS("../input_data/SFE_grid_yr_surv_031821.rds")

# Make "Year" a numeric variable
SFE_grid$Year <- as.numeric(SFE_grid$Year)

# Create scaled_year column in prediction grid
SFE_grid$scaled_year <- (SFE_grid$Year - mean(SFE_grid$Year)) / sd(SFE_grid$Year)

# Create 'Month' dataframe
Month <- tibble(Month = 1:12)

# Join Month and grid dataframes
t <- crossing(SFE_grid,Month)

t_1 <- t %>% slice(1:10610208)
t_2 <- t %>% slice(10610209:21220416)
t_3 <- t %>% slice(21220417:31830624)
t_4 <- t %>% slice(31830625:42440832)

# Remove unnecessary objects to free up computing power
rm(t)
rm(SFE_grid)
rm(pSTRBAS_SFES)
rm(pDELSME_SFES)
rm(pLONSME_SFES)
rm(pAMESHA_SFES)
rm(pTHRSHA_SFES)
rm(Month)
gc()

```

# Generate Predictions on a 500m x 500m grid of the estuary
Predict in slices - limited by ram

### Striped Bass Prediction

```{r}
# Generate predictions on slices
pSTRBAS_1 <- predict(mSTRBAS, newdata = t_1)
pSTRBAS_2 <- predict(mSTRBAS, newdata = t_2)
pSTRBAS_3 <- predict(mSTRBAS, newdata = t_3)
pSTRBAS_4 <- predict(mSTRBAS, newdata = t_4)

# Combine sliced predictions into single dataframe
pSTRBAS <- bind_rows(pSTRBAS_1,pSTRBAS_2,pSTRBAS_3,pSTRBAS_4)

# Save grid predictions
saveRDS(pSTRBAS, "../predictions/042022/pSTRBAS.rds")

# Generate a grid of decadal mean estimates from 1980-2017
pSTRBAS_mean <- pSTRBAS %>%
  mutate(decade = case_when(Year %in% 1980:1989 ~ "1980s",
                            Year %in% 1990:1999 ~ "1990s",
                            Year %in% 2000:2009 ~ "2000s",
                            Year %in% 2010:2017 ~ "2010s")) %>%
  group_by(X,Y,decade) %>%
  summarise(mean_est = mean(plogis(est)))

# Save decadal mean grid predictions
saveRDS(pSTRBAS_mean, "../predictions/042022/pSTRBAS_mean.rds")

# Remove slice predictions to free up computing space
rm(pSTRBAS_1)
rm(pSTRBAS_2)
rm(pSTRBAS_3)
rm(pSTRBAS_4)
rm(pSTRBAS)
rm(pSTRBAS_mean)
gc()
```

### Delta Smelt Prediction

```{r}
# Generate predictions on slices
pDELSME_1 <- predict(mDELSME, newdata = t_1)
pDELSME_2 <- predict(mDELSME, newdata = t_2)
pDELSME_3 <- predict(mDELSME, newdata = t_3)
pDELSME_4 <- predict(mDELSME, newdata = t_4)

# Combine sliced predictions into single dataframe
pDELSME <- bind_rows(pDELSME_1,pDELSME_2,pDELSME_3,pDELSME_4)

# Save grid predictions
saveRDS(pDELSME, "../predictions/042022/pDELSME.rds")

# Generate a grid of decadal mean estimates from 1980-2017
pDELSME_mean <- pDELSME %>%
  mutate(decade = case_when(Year %in% 1980:1989 ~ "1980s",
                            Year %in% 1990:1999 ~ "1990s",
                            Year %in% 2000:2009 ~ "2000s",
                            Year %in% 2010:2017 ~ "2010s")) %>%
  group_by(X,Y,decade) %>%
  summarise(mean_est = mean(plogis(est)))

# Save decadal mean grid predictions
saveRDS(pDELSME_mean, "../predictions/042022/pDELSME_mean.rds")

# Remove slice predictions to free up computing space
rm(pDELSME_1)
rm(pDELSME_2)
rm(pDELSME_3)
rm(pDELSME_4)
rm(pDELSME)
rm(pDELSME_mean)
gc()
```

### Longfin Smelt Prediction

```{r}
# Generate predictions on slices
pLONSME_1 <- predict(mLONSME, newdata = t_1)
pLONSME_2 <- predict(mLONSME, newdata = t_2)
pLONSME_3 <- predict(mLONSME, newdata = t_3)
pLONSME_4 <- predict(mLONSME, newdata = t_4)

# Combine sliced predictions into single dataframe
pLONSME <- bind_rows(pLONSME_1,pLONSME_2,pLONSME_3,pLONSME_4)

# Save grid predictions
saveRDS(pLONSME, "../predictions/042022/pLONSME.rds")

# Generate a grid of decadal mean estimates from 1980-2017
pLONSME_mean <- pLONSME %>%
  mutate(decade = case_when(Year %in% 1980:1989 ~ "1980s",
                            Year %in% 1990:1999 ~ "1990s",
                            Year %in% 2000:2009 ~ "2000s",
                            Year %in% 2010:2017 ~ "2010s")) %>%
  group_by(X,Y,decade) %>%
  summarise(mean_est = mean(plogis(est)))

# Save decadal mean grid predictions
saveRDS(pLONSME_mean, "../predictions/042022/pLONSME_mean.rds")

# Remove slice predictions to free up computing space
rm(pLONSME_1)
rm(pLONSME_2)
rm(pLONSME_3)
rm(pLONSME_4)
rm(pLONSME)
rm(pLONSME_mean)
gc()
```

### Threadfin Shad Prediction

```{r}
# Generate predictions on slices
pTHRSHA_1 <- predict(mTHRSHA, newdata = t_1)
pTHRSHA_2 <- predict(mTHRSHA, newdata = t_2)
pTHRSHA_3 <- predict(mTHRSHA, newdata = t_3)
pTHRSHA_4 <- predict(mTHRSHA, newdata = t_4)

# Combine sliced predictions into single dataframe
pTHRSHA <- bind_rows(pTHRSHA_1,pTHRSHA_2,pTHRSHA_3,pTHRSHA_4)

# Save grid predictions
saveRDS(pTHRSHA, "../predictions/042022/pTHRSHA.rds")

# Generate a grid of decadal mean estimates from 1980-2017
pTHRSHA_mean <- pTHRSHA %>%
  mutate(decade = case_when(Year %in% 1980:1989 ~ "1980s",
                            Year %in% 1990:1999 ~ "1990s",
                            Year %in% 2000:2009 ~ "2000s",
                            Year %in% 2010:2017 ~ "2010s")) %>%
  group_by(X,Y,decade) %>%
  summarise(mean_est = mean(plogis(est)))

# Save decadal mean grid predictions
saveRDS(pTHRSHA_mean, "../predictions/042022/pTHRSHA_mean.rds")

# Remove slice predictions to free up computing space
rm(pTHRSHA_1)
rm(pTHRSHA_2)
rm(pTHRSHA_3)
rm(pTHRSHA_4)
rm(pTHRSHA)
gc()
```

### American Shad Prediction

```{r}
# Generate predictions on slices
pAMESHA_1 <- predict(mAMESHA, newdata = t_1)
pAMESHA_2 <- predict(mAMESHA, newdata = t_2)
pAMESHA_3 <- predict(mAMESHA, newdata = t_3)
pAMESHA_4 <- predict(mAMESHA, newdata = t_4)

# Combine sliced predictions into single dataframe
pAMESHA <- bind_rows(pAMESHA_1,pAMESHA_2,pAMESHA_3,pAMESHA_4)

# Save grid predictions
saveRDS(pAMESHA, "../predictions/042022/pAMESHA.rds")

# Generate a grid of decadal mean estimates from 1980-2017
pAMESHA_mean <- pAMESHA %>%
  mutate(decade = case_when(Year %in% 1980:1989 ~ "1980s",
                            Year %in% 1990:1999 ~ "1990s",
                            Year %in% 2000:2009 ~ "2000s",
                            Year %in% 2010:2017 ~ "2010s")) %>%
  group_by(X,Y,decade) %>%
  summarise(mean_est = mean(plogis(est)))

# Save decadal mean grid predictions
saveRDS(pAMESHA_mean, "../predictions/042022/pAMESHA_mean.rds")

# Remove slice predictions to free up computing space
rm(pAMESHA_1)
rm(pAMESHA_2)
rm(pAMESHA_3)
rm(pAMESHA_4)
rm(pAMESHA)
gc()
```

# Join the prediction dataframes together for plotting overall abundance trends
The resulting dataframe is far too large to apply a ggplot gam smoother if prediction grids include all month and survey predictions. To deal with it, I take the mean estimate for each spatial point (X,Y) per year and then bind the individual dataframes together for plotting.

```{r}
# Read in prediction grids
pSTRBAS <- readRDS("../predictions/042022/pSTRBAS.rds")
pDELSME <- readRDS("../predictions/042022/pDELSME.rds")
pLONSME <- readRDS("../predictions/042022/pLONSME.rds")
pTHRSHA <- readRDS("../predictions/042022/pTHRSHA.rds")
pAMESHA <- readRDS("../predictions/042022/pAMESHA.rds")

# Take the yearly mean for each spatial point estimate
pSTRBAS_slim <- pSTRBAS %>%
  group_by(X,Y,Year) %>%
  summarize(est = mean(est))
pDELSME_slim <- pDELSME %>%
  group_by(X,Y,Year) %>%
  summarize(est = mean(est))
pLONSME_slim <- pLONSME %>%
  group_by(X,Y,Year) %>%
  summarize(est = mean(est))
pTHRSHA_slim <- pTHRSHA %>%
  group_by(X,Y,Year) %>%
  summarize(est = mean(est))
pAMESHA_slim <- pAMESHA %>%
  group_by(X,Y,Year) %>%
  summarize(est = mean(est))

# Add species column to each prediction
pSTRBAS_slim$species <- "STRBAS"
pDELSME_slim$species <- "DELSME"
pLONSME_slim$species <- "LONSME"
pTHRSHA_slim$species <- "THRSHA"
pAMESHA_slim$species <- "AMESHA"

# Bind the prediction grids together
pred_all_species <- bind_rows(pSTRBAS_slim,pDELSME_slim,pLONSME_slim,pTHRSHA_slim,pAMESHA_slim)

# Save all_species prediction grid
saveRDS(pred_all_species, "../predictions/042022/pred_all_species.rds")
```

# Generate prediction simulations for representing uncertainty of spatial slope estimates

Using 200 simulations - bootstrapping!

### First modify prediction grid for simulations

```{r}
# Read back in full prediction grid
t <- bind_rows(t_1,t_2,t_3,t_4)

# Remove sliced grid pieces
rm(t_1,t_2,t_3,t_4)
gc()

# Filter prediction grid to a single year since it should be the same slope prediction for every year
t_pred <- t %>% filter(Year == 2017)
```

### Striped Bass simulations

```{r}
# Read in model output
mSTRBAS <- readRDS("../output_models/042022/mSTRBAS.rds")

# Generate prediction simulation of zeta_s (spatial slope) 
pSTRBAS_sim <- predict(mSTRBAS, newdata = t_pred, sims = 200, sims_var = "zeta_s")

# Save prediction simulation
saveRDS(pSTRBAS_sim, "../predictions/042022/pSTRBAS_sim.rds")

# Read in prediction simulation and full prediction grid
pSTRBAS_sim <- readRDS("../predictions/042022/pSTRBAS_sim.rds")
pSTRBAS <- readRDS("../predictions/042022/pSTRBAS.rds")

# Filter prediction to just 2017
pSTRBAS_2017 <- pSTRBAS %>% filter(Year == 2017)

# Calculate summary statistics from simulation output
pSTRBAS_2017$median <- apply((pSTRBAS_sim), 1, median)
pSTRBAS_2017$lwr <- apply((pSTRBAS_sim), 1, quantile, probs = 0.025)
pSTRBAS_2017$upr <- apply((pSTRBAS_sim), 1, quantile, probs = 0.975)
pSTRBAS_2017$mean <- round(apply((pSTRBAS_sim), 1, mean),2)
pSTRBAS_2017$sd <- round(apply((pSTRBAS_sim), 1, sd),2)
pSTRBAS_2017$cv <- pSTRBAS_2017$sd/(pSTRBAS_2017$mean)

# Save prediction grid with newly added summary statistics
saveRDS(pSTRBAS_2017, "../predictions/042022/pSTRBAS_ss.rds")

# Remove predictions to free up ram
rm(pSTRBAS)
rm(pSTRBAS_2017)
rm(pSTRBAS_sim)
rm(mSTRBAS)
rm(t)
gc()
```

### Delta Smelt simulations

```{r}
# Read in model output
mDELSME <- readRDS("../output_models/042022/mDELSME.rds")

# Generate prediction simulation of zeta_s (spatial slope) 
pDELSME_sim <- predict(mDELSME, newdata = t_pred, sims = 200, sims_var = "zeta_s")

# Save prediction simulation
saveRDS(pDELSME_sim, "../predictions/042022/pDELSME_sim.rds")

# Read in prediction simulation and full prediction grid
pDELSME_sim <- readRDS("../predictions/042022/pDELSME_sim.rds")
pDELSME <- readRDS("../predictions/042022/pDELSME.rds")

# Filter prediction to just 2017
pDELSME_2017 <- pDELSME %>% filter(Year == 2017)

# Calculate summary statistics from simulation output
pDELSME_2017$median <- apply((pDELSME_sim), 1, median)
pDELSME_2017$lwr <- apply((pDELSME_sim), 1, quantile, probs = 0.025)
pDELSME_2017$upr <- apply((pDELSME_sim), 1, quantile, probs = 0.975)
pDELSME_2017$mean <- round(apply((pDELSME_sim), 1, mean),2)
pDELSME_2017$sd <- round(apply((pDELSME_sim), 1, sd),2)
pDELSME_2017$cv <- pDELSME_2017$sd/(pDELSME_2017$mean)

# Save prediction grid with newly added summary statistics
saveRDS(pDELSME_2017, "../predictions/042022/pDELSME_ss.rds")

# Remove predictions to free up ram
rm(pDELSME)
rm(pDELSME_2017)
rm(pDELSME_sim)
rm(mDELSME)
gc()
```

### Longfin Smelt simulations

```{r}
# Read in model output
mLONSME <- readRDS("../output_models/042022/mLONSME.rds")

# Generate prediction simulation of zeta_s (spatial slope) 
pLONSME_sim <- predict(mLONSME, newdata = t_pred, sims = 200, sims_var = "zeta_s")

# Save prediction simulation
saveRDS(pLONSME_sim, "../predictions/042022/pLONSME_sim.rds")

# Read in prediction simulation and full prediction grid
pLONSME_sim <- readRDS("../predictions/042022/pLONSME_sim.rds")
pLONSME <- readRDS("../predictions/042022/pLONSME.rds")

# Filter prediction to just 2017
pLONSME_2017 <- pLONSME %>% filter(Year == 2017)

# Calculate summary statistics from simulation output
pLONSME_2017$median <- apply((pLONSME_sim), 1, median)
pLONSME_2017$lwr <- apply((pLONSME_sim), 1, quantile, probs = 0.025)
pLONSME_2017$upr <- apply((pLONSME_sim), 1, quantile, probs = 0.975)
pLONSME_2017$mean <- round(apply((pLONSME_sim), 1, mean),2)
pLONSME_2017$sd <- round(apply((pLONSME_sim), 1, sd),2)
pLONSME_2017$cv <- pLONSME_2017$sd/(pLONSME_2017$mean)

# Save prediction grid with newly added summary statistics
saveRDS(pLONSME_2017, "../predictions/042022/pLONSME_ss.rds")

# Remove predictions to free up ram
rm(pLONSME)
rm(pLONSME_2017)
rm(pLONSME_sim)
rm(mLONSME)
gc()
```

### Threadfin Shad simulations

```{r}
# Read in model output
mTHRSHA <- readRDS("../output_models/042022/mTHRSHA.rds")

# Generate prediction simulation of zeta_s (spatial slope) 
pTHRSHA_sim <- predict(mTHRSHA, newdata = t_pred, sims = 200, sims_var = "zeta_s")

# Save prediction simulation
saveRDS(pTHRSHA_sim, "../predictions/042022/pTHRSHA_sim.rds")

# Read in prediction simulation and full prediction grid
pTHRSHA_sim <- readRDS("../predictions/042022/pTHRSHA_sim.rds")
pTHRSHA <- readRDS("../predictions/042022/pTHRSHA.rds")

# Filter prediction to just 2017
pTHRSHA_2017 <- pTHRSHA %>% filter(Year == 2017)

# Calculate summary statistics from simulation output
pTHRSHA_2017$median <- apply((pTHRSHA_sim), 1, median)
pTHRSHA_2017$lwr <- apply((pTHRSHA_sim), 1, quantile, probs = 0.025)
pTHRSHA_2017$upr <- apply((pTHRSHA_sim), 1, quantile, probs = 0.975)
pTHRSHA_2017$mean <- round(apply((pTHRSHA_sim), 1, mean),2)
pTHRSHA_2017$sd <- round(apply((pTHRSHA_sim), 1, sd),2)
pTHRSHA_2017$cv <- pTHRSHA_2017$sd/(pTHRSHA_2017$mean)

# Save prediction grid with newly added summary statistics
saveRDS(pTHRSHA_2017, "../predictions/042022/pTHRSHA_ss.rds")

# Remove predictions to free up ram
rm(pTHRSHA)
rm(pTHRSHA_2017)
rm(pTHRSHA_sim)
rm(mTHRSHA)
gc()
```

### American Shad simulations

```{r}
# Read in model output
mAMESHA <- readRDS("../output_models/042022/mAMESHA.rds")

# Generate prediction simulation of zeta_s (spatial slope) 
pAMESHA_sim <- predict(mAMESHA, newdata = t_pred, sims = 200, sims_var = "zeta_s")

# Save prediction simulation
saveRDS(pAMESHA_sim, "../predictions/042022/pAMESHA_sim.rds")

# Read in prediction simulation and full prediction grid
pAMESHA_sim <- readRDS("../predictions/042022/pAMESHA_sim.rds")
pAMESHA <- readRDS("../predictions/042022/pAMESHA.rds")

# Filter prediction to just 2017
pAMESHA_2017 <- pAMESHA %>% filter(Year == 2017)

# Calculate summary statistics from simulation output
pAMESHA_2017$median <- apply((pAMESHA_sim), 1, median)
pAMESHA_2017$lwr <- apply((pAMESHA_sim), 1, quantile, probs = 0.025)
pAMESHA_2017$upr <- apply((pAMESHA_sim), 1, quantile, probs = 0.975)
pAMESHA_2017$mean <- round(apply((pAMESHA_sim), 1, mean),2)
pAMESHA_2017$sd <- round(apply((pAMESHA_sim), 1, sd),2)
pAMESHA_2017$cv <- pAMESHA_2017$sd/(pAMESHA_2017$mean)

# Save prediction grid with newly added summary statistics
saveRDS(pAMESHA_2017, "../predictions/042022/pAMESHA_ss.rds")

# Remove predictions to free up ram
rm(pAMESHA)
rm(pAMESHA_2017)
rm(pAMESHA_sim)
rm(mAMESHA)
gc()
```

### Generate center of gravity predicitons

```{r}
# Read in predictions on SFES survey points
pSTRBAS_SFES <- readRDS("../predictions/042022/pSTRBAS_SFES.rds")
pDELSME_SFES <- readRDS("../predictions/042022/pDELSME_SFES.rds")
pLONSME_SFES <- readRDS("../predictions/042022/pLONSME_SFES.rds")
pTHRSHA_SFES <- readRDS("../predictions/042022/pTHRSHA_SFES.rds")
pAMESHA_SFES <- readRDS("../predictions/042022/pAMESHA_SFES.rds")

# Striped Bass
cog_STRBAS <- get_cog(pSTRBAS_SFES, level = 0.95)

# Delta Smelt
cog_DELSME <- get_cog(pDELSME_SFES, level = 0.95)

# Longfin Smelt
cog_LONSME <- get_cog(pLONSME_SFES, level = 0.95)

# Threadfin Shad
cog_THRSHA <- get_cog(pTHRSHA_SFES, level = 0.95)

# American Shad
cog_AMESHA <- get_cog(pAMESHA_SFES, level = 0.95)

# Save center of gravity dataframes
saveRDS(cog_STRBAS, "../COG/042022/cog_STRBAS.rds")
saveRDS(cog_DELSME, "../COG/042022/cog_DELSME.rds")
saveRDS(cog_LONSME, "../COG/042022/cog_LONSME.rds")
saveRDS(cog_THRSHA, "../COG/042022/cog_THRSHA.rds")
saveRDS(cog_AMESHA, "../COG/042022/cog_AMESHA.rds")

# Read center of gravity dataframes
cog_STRBAS <- readRDS("../COG/042022/cog_STRBAS.rds")
cog_DELSME <- readRDS("../COG/042022/cog_DELSME.rds")
cog_LONSME <- readRDS("../COG/042022/cog_LONSME.rds")
cog_THRSHA <- readRDS("../COG/042022/cog_THRSHA.rds")
cog_AMESHA <- readRDS("../COG/042022/cog_AMESHA.rds")
```

### Generate COG GAM and join to outflow dataframe for plotting

Generate a simple GAM for showing trends in COG plus effects of outflow

```{r}
# Read in required packages
library(mgcv)
library(tidymv)

# Read in outflow data. Sourced from DWR dayflow
outflow <- readRDS("../Input_data/outflow_annual.RDS")

# Filter outflow to the years we model
outflow_trim <- outflow %>%
  filter(Year %in% 1980:2017)

# add species identifier to cog dataframes
cog_STRBAS$species <- "STRBAS"
cog_DELSME$species <- "DELSME"
cog_LONSME$species <- "LONSME"
cog_THRSHA$species <- "THRSHA"
cog_AMESHA$species <- "AMESHA"

# Join cog dataframes
cog <- full_join(cog_STRBAS,cog_DELSME)
cog <- full_join(cog,cog_LONSME)
cog <- full_join(cog,cog_THRSHA)
cog <- full_join(cog,cog_AMESHA)

# Estimate standard deviation from 95% confidence interval, select only X (latitudinal) coordinates
cog <- cog %>%
  mutate(sd = ((upr-lwr)/2)*1.96) %>%
  filter(coord == "X")

# Join Outflow data to center of gravity predictions, add variance column for GAM modeling (weights arg)
cog_of <- full_join(cog,outflow_trim) %>%
  mutate(species = as.factor(species), 
         var = (sd)^2)

# Run a GAM of estimated COG predicted by smooth year and outflow by species, plus species as a linear fixed effect
mCOG <- mgcv::gam(data = cog_of, est ~ s(Year, by = species) + s(outflow_maf, by = species) + species, weights = var)

# Summarize model results
summary(mCOG)

# Save model
saveRDS(mCOG, file = "../COG/021523/mCOG.rds")

# Generate predicted smooth fit and standard error of COG on cog_of dataframe
pCOG <- as.data.frame(mgcv::predict.gam(mCOG, newdata = cog_of, se.fit = T))

# Add ID column for joining GAM fit and cog_of dataframes
cog_of$ID <- c(1:190)
pCOG$ID <- c(1:190)

# Join the pCOG and cog_of dataframes together for plotting
cog_fit <- full_join(cog_of,pCOG, by = "ID")

# Save fit of COG dataframe
saveRDS(cog_fit, file = "../COG/021523/cog_fit.rds")
```