---
title: "model_building"
author: "Dylan K Stompe"
date: "03/02/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup}
library(sf)
library(tidyverse)
library(sdmTMB)
library(geoR)
library(DHARMa)
```

# Read and manipulate data prior to analysis
### Read in datasets

```{r read in data}
# Read in SFES data
SFES <- readRDS("../Input_data/SFES_111621.rds")
```

### Clean up the source data a little bit

```{r data cleanup}
# Change 'survey' to a factor variable
SFES$Survey <- as.factor(SFES$Survey)

# Filter out upstream Sac River sites
### Too distant to be meaningfull in model construction
SR_filter <- c("SR060E","AM001S","SR049E","SR043W","SR144W","SR138E","SR130E","SR119E","SR094E","SR090W","SR080E","FW1")
SFES <- SFES %>%
  filter(!Station %in% SR_filter)

# Make 'Month' a numeric variable for model construction
SFES$Month <- as.numeric(SFES$Month)

# Set up a column for time that is Normal(0,1) to help with estimation
# This is required for modeling trends - i.e. slope
SFES$scaled_year <- (SFES$Year - mean(SFES$Year)) / sd(SFES$Year)
```

### Start cleaning up and projecting spatial data

```{r project spatial data}
# Set projection - UTM zone 10N
crs_utm10 <- 32610

# Project survey data coordinates (crs = 4326 corresponds to WGS84)

SFES_proj <- SFES %>% select(Longitude, Latitude) %>% #SFES df
  st_as_sf(crs = 4326, coords = c("Longitude", "Latitude")) %>%
  st_transform(crs_utm10)

# Extract station UTM coordinates:

SFES_utm_coords <- st_coordinates(SFES_proj)

# Append UTM coordinates to dataframe - scale coordinates to km so the range parameter is on a reasonable scale for estimation:

SFES$X <- SFES_utm_coords[,1] / 1000 
SFES$Y <- SFES_utm_coords[,2] / 1000 

# Save cleaned up SFES file
# saveRDS(SFES, "../input_data/SFES_clean_080222.rds", compress = TRUE)
```

### Generate spatial meshes
Knot cutoff distance set to 2km to minimize overfitting in heavily sampled portions of the estuary.
Cutoff iteratively determined based on model fit.

```{r generate mesh}
# Generate a mesh
spde_SFES <- make_mesh(SFES, xy_cols = c("X", "Y"),
                       type = "cutoff",
                       cutoff = 2) # Cutoff distance of 2km

# Inspect mesh
plot(spde_SFES)

# Save mesh for later plotting
saveRDS(spde_SFES, "../input_data/spde_SFES.rds")
```

### Read in barrier polygon and constrain spatial mesh

```{r add barrier to mesh}
# Read in barrier polygon
SFE_polygon_ubersimple <- st_read("../input_data/SFE_Barrier_ubersimple1/SFE_Barrier_ubersimple1.shp")

# Add UTM projection using st_transform
SFE_polygon_ubersimple <- st_transform(SFE_polygon_ubersimple, crs_utm10)

# Add on the barrier mesh component:
bspde_SFES <- add_barrier_mesh(
  spde_SFES, SFE_polygon_ubersimple, proj_scaling = 1000, range_fraction = .1,
  plot = TRUE)

# Save and read in bspde_SFES for faster setup before model building
#saveRDS(bspde_SFES, "../input_data/bspde_SFES.rds")
 bspde_SFES <- readRDS("../input_data/bspde_SFES.rds")
```

# 8-Survey (SFES) Dataset Analysis

The following code analyzes the spatial variation in density using the 8-survey index dataset. This dataset includes 8 long-term surveys, from 1980 to 2017, and only includes continuously sampled stations. 

### Remove clutter to assist with computational efficiency

```{r}
rm(spde_SFES)
rm(SFES_proj)
rm(SFES_utm_coords)
gc()
```

### Build models with SFES dataset 

Model species distribution using multiple intercepts, spatial random effects, and Survey as a fixed effect. Binomial distribution with a logit-link function used to remove scaling error due to differential capture efficiency. Modeling presence distills fixed effect of Survey to a single dimension.

### Build striped bass models

```{r build STRBAS models}
## Striped Bass distribution model

# Add a column of 0/1 (no catch/catch)

SFES$STRBAS_bin <- ifelse(SFES$STRBAS > 0, 1, 0)

# Striped bass model 
# survey, smoothed month, and scaled_year as predictor variables 
# binomial distribution with logit link function applied

 mSTRBAS <- sdmTMB(STRBAS_bin ~ Survey + s(Month, bs="cr"),
                   data = SFES,
                   mesh = bspde_SFES, 
                   family = binomial(link = "logit"),
                   spatial = "on",
                   spatiotemporal = "IID",
                   time = "Year",
                   spatial_varying = ~ 0 + scaled_year,
                   silent = FALSE)
 
mSTRBAS <- run_extra_optimization(mSTRBAS) # Converged 4/20/22
 
 saveRDS(mSTRBAS, "../output_models/042022/mSTRBAS.rds")

mSTRBAS <- readRDS("../output_models/042022/mSTRBAS.rds")
```

### Build Delta smelt models

```{r build DELSME models}
## Delta Smelt distribution model

# Add a column of 0/1 (no catch/catch)

SFES$DELSME_bin <- ifelse(SFES$DELSME > 0, 1, 0)

# Delta Smelt model 
# survey, smoothed month, and scaled_year as predictor variables 
# binomial distribution with logit link function applied

mDELSME <- sdmTMB(DELSME_bin ~ Survey + s(Month, bs = "cr"), # Converged 4/20/22
                   data = SFES,
                   mesh = bspde_SFES, 
                   family = binomial(link = "logit"),
                   spatial = "on",
                   spatiotemporal = "IID",
                   time = "Year",
                   spatial_varying = ~ 0 + scaled_year,
                   silent = FALSE)

saveRDS(mDELSME, "../output_models/042022/mDELSME.rds")

mDELSME <- readRDS("../output_models/042022/mDELSME.rds")
```

### Build Longfin smelt models

```{r build LONSME models}
## Longfin Smelt distribution model

# Add a column of 0/1 (no catch/catch)

SFES$LONSME_bin <- ifelse(SFES$LONSME > 0, 1, 0)

# Longfin Smelt model 
# survey, smoothed month, and scaled_year as predictor variables 
# binomial distribution with logit link function applied

mLONSME <- sdmTMB(LONSME_bin ~ Survey + s(Month, bs="cr"),
                   data = SFES,
                   mesh = bspde_SFES, 
                   family = binomial(link = "logit"),
                   spatial = "on",
                   spatiotemporal = "IID",
                   time = "Year",
                   spatial_varying = ~ 0 + scaled_year,
                   silent = FALSE)

mLONSME <- run_extra_optimization(mLONSME) # Converged on 4/20/22

 saveRDS(mLONSME, "../output_models/042022/mLONSME.rds")

mLONSME <- readRDS("../output_models/042022/mLONSME.rds")
```

### Build Threadfin Shad models

```{r build THRSHA models}
## Threadfin Shad distribution model

# Add a column of 0/1 (no catch/catch)

SFES$THRSHA_bin <- ifelse(SFES$THRSHA > 0, 1, 0)

# Threadfin Shad model 
# survey, smoothed month, and scaled_year as predictor variables 
# binomial distribution with logit link function applied

 mTHRSHA <- sdmTMB(THRSHA_bin ~ Survey + s(Month, bs="cr"), # Converged on 4/20/22
                   data = SFES,
                   mesh = bspde_SFES, 
                   family = binomial(link = "logit"),
                   spatial = "on",
                   spatiotemporal = "IID",
                   time = "Year",
                   spatial_varying = ~ 0 + scaled_year,
                   silent = FALSE)

 saveRDS(mTHRSHA, "../output_models/042022/mTHRSHA.rds")

mTHRSHA <- readRDS("../output_models/032522/mTHRSHA.rds")
```

### Build American Shad models

```{r build AMESHA models}
## American Shad distribution model

# Add a column of 0/1 (no catch/catch)

SFES$AMESHA_bin <- ifelse(SFES$AMESHA > 0, 1, 0)

# American Shad model 
# survey, smoothed month, and scaled_year as predictor variables 
# binomial distribution with logit link function applied

 mAMESHA <- sdmTMB(AMESHA_bin ~ Survey + s(Month, bs="cr"), # Converged 4/20/22
                   data = SFES,
                   mesh = bspde_SFES, 
                   family = binomial(link = "logit"),
                   spatial = "on",
                   spatiotemporal = "IID",
                   time = "Year",
                   spatial_varying = ~ 0 + scaled_year,
                   silent = FALSE)

 saveRDS(mAMESHA, "../output_models/042022/mAMESHA.rds")

mAMESHA <- readRDS("../output_models/042022/mAMESHA.rds")
```

### Check model fit
Checking the model fit through simulation based residual sampling

```{r check model residuals fit}

# Striped Bass

pred_fixed_STRBAS <- mSTRBAS$family$linkinv(predict(mSTRBAS)$est_non_rf)

s_STRBAS <- simulate(mSTRBAS, nsim = 500)

STRBAS_test <- DHARMa::createDHARMa(
  simulatedResponse = s_STRBAS,
  observedResponse = SFES$STRBAS_bin,
  fittedPredictedResponse = pred_fixed_STRBAS
)

testResiduals(STRBAS_test)

saveRDS(STRBAS_test, "../model_diagnostics/050222/STRBAS_test.rds")

# Delta Smelt

pred_fixed_DELSME <- mDELSME$family$linkinv(predict(mDELSME)$est_non_rf)

s_DELSME <- simulate(mDELSME, nsim = 500)

DELSME_test <- DHARMa::createDHARMa(
  simulatedResponse = s_DELSME,
  observedResponse = SFES$DELSME_bin,
  fittedPredictedResponse = pred_fixed_DELSME
)

testResiduals(DELSME_test)

saveRDS(DELSME_test, "../model_diagnostics/050222/DELSME_test.rds")

# Longfin Smelt

pred_fixed_LONSME <- mLONSME$family$linkinv(predict(mLONSME)$est_non_rf)

s_LONSME <- simulate(mLONSME, nsim = 500)

LONSME_test <- DHARMa::createDHARMa(
  simulatedResponse = s_LONSME,
  observedResponse = SFES$LONSME_bin,
  fittedPredictedResponse = pred_fixed_LONSME
)

testResiduals(LONSME_test)

saveRDS(LONSME_test, "../model_diagnostics/050222/LONSME_test.rds")

# Threadfin Shad

pred_fixed_THRSHA <- mTHRSHA$family$linkinv(predict(mTHRSHA)$est_non_rf)

s_THRSHA <- simulate(mTHRSHA, nsim = 500)

THRSHA_test <- DHARMa::createDHARMa(
  simulatedResponse = s_THRSHA,
  observedResponse = SFES$THRSHA_bin,
  fittedPredictedResponse = pred_fixed_THRSHA
)

testResiduals(THRSHA_test)

saveRDS(THRSHA_test, "../model_diagnostics/050222/THRSHA_test.rds")

# American Shad

pred_fixed_AMESHA <- mAMESHA$family$linkinv(predict(mAMESHA)$est_non_rf)

s_AMESHA <- simulate(mAMESHA, nsim = 500)

AMESHA_test <- DHARMa::createDHARMa(
  simulatedResponse = s_AMESHA,
  observedResponse = SFES$AMESHA_bin,
  fittedPredictedResponse = pred_fixed_AMESHA
)

testResiduals(AMESHA_test)
testDispersion(AMESHA_test)


saveRDS(AMESHA_test, "../model_diagnostics/050222/AMESHA_test.rds")
```

The qqplots of residuals look good. The tests show significant deviation in some of the outlier/dispersion tests, however, the actual fits and number of outliers are not concerning. This is probably because there are so many data points.
