---
title: "paper_figures"
author: "Dylan K. Stompe"
date: "3/18/2022"
output: html_document
---

```{r setup}
library(sf)
library(tidyverse)
library(geoR)
library(ggpubr)
library(tidymv)
```

# Read in water-year, outflow data, and SFE polygon data

```{r}
# Read in water year type. Sourced from: https://cdec.water.ca.gov/reportapp/javareports?name=WSIHIST
wy <- read_csv("../Input_data/water_year.csv")

# Read in outflow data. Sourced from DWR dayflow
outflow <- readRDS("../Input_data/outflow_annual.RDS")

# Read in SFE Polygon data
SFE_polygon_ubersimple <- st_read("../input_data/SFE_Barrier_ubersimple1/SFE_Barrier_ubersimple1.shp")

# Set projection - UTM zone 10N
crs_utm10 <- 32610

# Add UTM projection using st_transform
SFE_polygon_ubersimple <- st_transform(SFE_polygon_ubersimple, crs_utm10)
```

# Figure 1

Figure of barrier mesh with land/water mesh vertices (knots) shown
bspde = barrier stochastic partial differential equation

```{r}
# Read in barrier spatial mesh
bspde_SFES <- readRDS("../input_data/bspde_SFES.rds")

# Print the total number of knots, knots in water, and knots on land
bspde_SFES$mesh$n # total number of knots

# Pull out centers of normal (water) and barrier (land) triangles
mesh_df_water <- bspde_SFES$mesh_sf[bspde_SFES$normal_triangles, ] # mesh triangles without restricted spatial correlation
mesh_df_land <- bspde_SFES$mesh_sf[bspde_SFES$barrier_triangles, ] # mesh triangles with restricted spatial correlation (range = 0.1)

# Generate a plot of the barrier mesh and mesh triangles:
barrier_plot <- ggplot(SFE_polygon_ubersimple) +
  theme_classic() +
  geom_sf() +
  geom_sf(data = mesh_df_water, size = 1, colour = "blue") +
  geom_sf(data = mesh_df_land, size = 1, colour = "green") +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) +
  ylab("Latitude") +
  xlab("Longitude")

barrier_plot

# Save the figure
ggsave(plot = barrier_plot, filename = "../Figures/042022/barrier_plot.png")
```


# Figure 2a

Striped Bass mean estimates of prob. of detection by decade

```{r}
# Read in mean prediction grids
pSTRBAS_mean <- readRDS("../predictions/042022/pSTRBAS_mean.rds")

# Striped Bass mean estimate of prob of detection by decade
STRBAS_est <- pSTRBAS_mean %>%
  ggplot() +
  geom_raster(aes(X*1000,Y*1000,fill=mean_est)) +
  scale_fill_viridis_c(name = "Probability of Detection", option = "magma", trans = "sqrt", breaks = c(0.05, 0.30, 0.80)) +
  theme_classic2() +
  geom_sf(data=SFE_polygon_ubersimple, colour = NA) +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) +
  ggtitle("Striped Bass") +
  theme(legend.position = c(0.17,0.2),
        axis.text.y = element_text(size = 6),
        axis.text.x = element_text(size = 6, angle = 45, vjust = 0.5, hjust = 0.5),
        legend.key.width = unit(.17, "in"),
        legend.key.height = unit (.15, "in"),
        legend.direction = "horizontal",
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 6, hjust = 0.5),
        legend.background = element_rect(fill = "grey90", color = NA),
        panel.background = element_rect(fill = 'grey90'),
        plot.title = element_text(hjust = 0.5)) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5)) +
  xlab("") +
  ylab("") +
  facet_grid(~decade)

STRBAS_est

ggsave("../Figures/042022/STRBAS_est.png", width = 8, height = 4, dpi = 600)
```

# Figure 2b

Delta Smelt mean estimates of prob. of detection by decade

```{r}
# Read in mean prediction grids
pDELSME_mean <- readRDS("../predictions/032822/pDELSME_mean.rds")

# Delta smelt mean estimate of prob of detection by decade
DELSME_est <- pDELSME_mean %>%
  ggplot() +
  geom_raster(aes(X*1000,Y*1000,fill=mean_est)) +
  scale_fill_viridis_c(name = "Probability of Detection", option = "magma", trans = "sqrt", breaks = c(0.05, 0.30, 0.8)) +
  theme_classic2() +
  geom_sf(data=SFE_polygon_ubersimple, colour = NA) +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) +
  ggtitle("Delta Smelt") +
  theme(legend.position = c(0.17,0.2),
        axis.text.y = element_text(size = 6),
        axis.text.x = element_text(size = 6, angle = 45, vjust = 0.5, hjust = 0.5),
        legend.key.width = unit(.17, "in"),
        legend.key.height = unit (.15, "in"),
        legend.direction = "horizontal",
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 6, hjust = 0.5),
        legend.background = element_rect(fill = "grey90", color = NA),
        panel.background = element_rect(fill = 'grey90'),
        plot.title = element_text(hjust = 0.5)) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5)) +
  xlab("") +
  ylab("") +
  facet_grid(~decade)

DELSME_est

ggsave("../Figures/032822/DELSME_est.png", width = 8, height = 4, dpi = 600)
```

# Figure 2c

Longfin smelt mean estimates of prob. of detection by decade

```{r}
# Read in mean prediction grids
pLONSME_mean <- readRDS("../predictions/032822/pLONSME_mean.rds")

# Longfin smelt mean estimate of prob of detection by decade
LONSME_est <- pLONSME_mean %>%
  ggplot() +
  geom_raster(aes(X*1000,Y*1000,fill=mean_est)) +
  scale_fill_viridis_c(name = "Probability of Detection", option = "magma", trans = "sqrt", breaks = c(0.05, 0.2, 0.50)) +
  theme_classic2() +
  geom_sf(data=SFE_polygon_ubersimple, colour = NA) +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) +
  ggtitle("Longfin Smelt") +
  theme(legend.position = c(0.17,0.2),
        axis.text.y = element_text(size = 6),
        axis.text.x = element_text(size = 6, angle = 45, vjust = 0.5, hjust = 0.5),
        legend.key.width = unit(.17, "in"),
        legend.key.height = unit (.15, "in"),
        legend.direction = "horizontal",
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 6, hjust = 0.5),
        legend.background = element_rect(fill = "grey90", color = NA),
        panel.background = element_rect(fill = 'grey90'),
        plot.title = element_text(hjust = 0.5)) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5)) +
  xlab("") +
  ylab("") +
  facet_grid(~decade)

LONSME_est

ggsave("../Figures/032822/LONSME_est.png", width = 8, height = 4, dpi = 600)
```

# Figure 2d

Threadfin Shad mean estimates of prob. of detection by decade

```{r}
# Read in mean prediction grids
pTHRSHA_mean <- readRDS("../predictions/032822/pTHRSHA_mean.rds")

# Threadfin shad mean estimate of prob of detection by decade
THRSHA_est <- pTHRSHA_mean %>%
  ggplot() +
  geom_raster(aes(X*1000,Y*1000,fill=mean_est)) +
  scale_fill_viridis_c(name = "Probability of Detection", option = "magma", trans = "sqrt", breaks = c(0.05, 0.30, 0.75)) +
  theme_classic2() +
  geom_sf(data=SFE_polygon_ubersimple, colour = NA) +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) +
  ggtitle("Threadfin Shad") +
  theme(legend.position = c(0.17,0.2),
        axis.text.y = element_text(size = 6),
        axis.text.x = element_text(size = 6, angle = 45, vjust = 0.5, hjust = 0.5),
        legend.key.width = unit(.17, "in"),
        legend.key.height = unit (.15, "in"),
        legend.direction = "horizontal",
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 6, hjust = 0.5),
        legend.background = element_rect(fill = "grey90", color = NA),
        panel.background = element_rect(fill = 'grey90'),
        plot.title = element_text(hjust = 0.5)) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5)) +
  xlab("") +
  ylab("") +
  facet_grid(~decade)

THRSHA_est

ggsave("../Figures/032822/THRSHA_est.png", width = 8, height = 4, dpi = 600)
```

# Figure 2f

American Shad mean estimates of prob. of detection by decade

```{r}
# Read in mean prediction grids
pAMESHA_mean <- readRDS("../predictions/032822/pAMESHA_mean.rds")

# American shad mean estimate of prob of detection by decade
AMESHA_est <- pAMESHA_mean %>%
  ggplot() +
  geom_raster(aes(X*1000,Y*1000,fill=mean_est)) +
  scale_fill_viridis_c(name = "Probability of Detection", option = "magma", trans = "sqrt", breaks = c(0.05, 0.20, 0.50)) +
  theme_classic2() +
  geom_sf(data=SFE_polygon_ubersimple, colour = NA) +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) +
  ggtitle("American Shad") +
  theme(legend.position = c(0.17,0.2),
        axis.text.y = element_text(size = 6),
        axis.text.x = element_text(size = 6, angle = 45, vjust = 0.5, hjust = 0.5),
        legend.key.width = unit(.17, "in"),
        legend.key.height = unit (.15, "in"),
        legend.direction = "horizontal",
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 6, hjust = 0.5),
        legend.background = element_rect(fill = "grey90", color = NA),
        panel.background = element_rect(fill = 'grey90'),
        plot.title = element_text(hjust = 0.5)) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5)) +
  xlab("") +
  ylab("") +
  facet_grid(~decade)

AMESHA_est

ggsave("../Figures/032822/AMESHA_est.png", width = 8, height = 4, dpi = 600)
```

# Figure 2

Generate all decade facet plots then save

```{r}
# Read in mean prediction grids
pSTRBAS_mean <- readRDS("../predictions/042022/pSTRBAS_mean.rds")
pDELSME_mean <- readRDS("../predictions/042022/pDELSME_mean.rds")
pLONSME_mean <- readRDS("../predictions/042022/pLONSME_mean.rds")
pTHRSHA_mean <- readRDS("../predictions/042022/pTHRSHA_mean.rds")
pAMESHA_mean <- readRDS("../predictions/042022/pAMESHA_mean.rds")


#STRBAS
STRBAS_est <- pSTRBAS_mean %>%
  ggplot() +
  geom_raster(aes(X*1000,Y*1000,fill=mean_est)) +
  scale_fill_viridis_c(name = "Probability of Detection", option = "magma", trans = "sqrt", breaks = c(0.05, 0.30, 0.80)) +
  theme_classic2() +
  geom_sf(data=SFE_polygon_ubersimple, colour = NA) +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) +
  theme(legend.position = c(0.17,0.2),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size = 8),
        legend.key.width = unit(.17, "in"),
        legend.key.height = unit (.15, "in"),
        legend.direction = "horizontal",
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 6, hjust = 0.5),
        legend.background = element_rect(fill = "grey90", color = NA),
        panel.background = element_rect(fill = 'grey90'),
        plot.title = element_text(hjust = 0.5)) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5)) +
  xlab("") +
  ylab("") +
  facet_grid(~decade) +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank())

#DELSME
DELSME_est <- pDELSME_mean %>%
  ggplot() +
  geom_raster(aes(X*1000,Y*1000,fill=mean_est)) +
  scale_fill_viridis_c(name = "Probability of Detection", option = "magma", trans = "sqrt", breaks = c(0.05, 0.30, 0.8)) +
  theme_classic2() +
  geom_sf(data=SFE_polygon_ubersimple, colour = NA) +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) +
  theme(legend.position = c(0.17,0.2),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size = 8),
        legend.key.width = unit(.17, "in"),
        legend.key.height = unit (.15, "in"),
        legend.direction = "horizontal",
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 6, hjust = 0.5),
        legend.background = element_rect(fill = "grey90", color = NA),
        panel.background = element_rect(fill = 'grey90'),
        plot.title = element_text(hjust = 0.5)) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5)) +
  xlab("") +
  ylab("") +
  facet_grid(~decade) +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank())

#LONSME
LONSME_est <- pLONSME_mean %>%
  ggplot() +
  geom_raster(aes(X*1000,Y*1000,fill=mean_est)) +
  scale_fill_viridis_c(name = "Probability of Detection", option = "magma", trans = "sqrt", breaks = c(0.05, 0.2, 0.50)) +
  theme_classic2() +
  geom_sf(data=SFE_polygon_ubersimple, colour = NA) +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) +
  theme(legend.position = c(0.17,0.2),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size = 8),
        legend.key.width = unit(.17, "in"),
        legend.key.height = unit (.15, "in"),
        legend.direction = "horizontal",
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 6, hjust = 0.5),
        legend.background = element_rect(fill = "grey90", color = NA),
        panel.background = element_rect(fill = 'grey90'),
        plot.title = element_text(hjust = 0.5)) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5)) +
  xlab("") +
  ylab("") +
  facet_grid(~decade) +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank())

#THRSHA
THRSHA_est <- pTHRSHA_mean %>%
  ggplot() +
  geom_raster(aes(X*1000,Y*1000,fill=mean_est)) +
  scale_fill_viridis_c(name = "Probability of Detection", option = "magma", trans = "sqrt", breaks = c(0.05, 0.30, 0.75)) +
  theme_classic2() +
  geom_sf(data=SFE_polygon_ubersimple, colour = NA) +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) +
  theme(legend.position = c(0.17,0.2),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size = 8),
        legend.key.width = unit(.17, "in"),
        legend.key.height = unit (.15, "in"),
        legend.direction = "horizontal",
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 6, hjust = 0.5),
        legend.background = element_rect(fill = "grey90", color = NA),
        panel.background = element_rect(fill = 'grey90'),
        plot.title = element_text(hjust = 0.5)) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5)) +
  xlab("") +
  ylab("") +
  facet_grid(~decade) +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank())

#AMESHA
AMESHA_est <- pAMESHA_mean %>%
  ggplot() +
  geom_raster(aes(X*1000,Y*1000,fill=mean_est)) +
  scale_fill_viridis_c(name = "Probability of Detection", option = "magma", trans = "sqrt", breaks = c(0.05, 0.20, 0.50)) +
  theme_classic2() +
  geom_sf(data=SFE_polygon_ubersimple, colour = NA) +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) +
  theme(legend.position = c(0.17,0.2),
        axis.text.y = element_text(size = 8),
        axis.text.x = element_text(size = 8, angle = 45, vjust = 0.5, hjust = 0.5),
        legend.key.width = unit(.17, "in"),
        legend.key.height = unit (.15, "in"),
        legend.direction = "horizontal",
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 6, hjust = 0.5),
        legend.background = element_rect(fill = "grey90", color = NA),
        panel.background = element_rect(fill = 'grey90'),
        plot.title = element_text(hjust = 0.5)) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5)) +
  xlab("") +
  ylab("") +
  facet_grid(~decade) +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank())

# Aligning not working well with ggarrange so save them separately then put them together in post
ggsave("../Figures/042022/STRBAS_est.png", plot = STRBAS_est, width = 8, height = 4, dpi = 600)
ggsave("../Figures/042022/DELSME_est.png", plot = DELSME_est, width = 8, height = 4, dpi = 600)
ggsave("../Figures/042022/LONSME_est.png", plot = LONSME_est, width = 8, height = 4, dpi = 600)
ggsave("../Figures/042022/THRSHA_est.png", plot = THRSHA_est, width = 8, height = 4, dpi = 600)
ggsave("../Figures/042022/AMESHA_est.png", plot = AMESHA_est, width = 8, height = 4, dpi = 600)
```

# Figure 3

Save the species component plots then hack them all together in powerpoint #peakcoding

### Striped Bass components - 3a

```{r}
# Read in Striped Bass predictions
pSTRBAS_2017 <- readRDS("../predictions/042022/pSTRBAS_ss.rds")

# Striped Bass slope
STRBAS_slope <- pSTRBAS_2017 %>%
  ggplot() +
  geom_raster(aes(X*1000,Y*1000,fill=zeta_s)) +
  scale_fill_gradient2(
  low = "red",
  mid = "white",
  high = "blue",
  midpoint = 0,
  limits = c(-2,2),
  name = "Spatial Slope") +
  theme_classic2() +
  geom_sf(data=SFE_polygon_ubersimple, colour = NA) +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) +
  theme(legend.position = c(0.72,0.2),
        axis.text.y = element_text(size = 8),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.key.width = unit(.2, "in"),
        legend.key.height = unit (.15, "in"),
        legend.direction = "horizontal",
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.background = element_rect(fill = "grey90", color = NA),
        panel.background = element_rect(fill = 'grey90')) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5)) +
  xlab("") +
  ylab("")

#STRBAS_slope

# Striped Bass slope standard deviation
STRBAS_sd <- pSTRBAS_2017 %>%
  ggplot() +
  geom_raster(aes(X*1000,Y*1000,fill=sd)) +
  scale_fill_viridis_c(name = "Spatial Slope SD") +
  theme_classic2() +
  geom_sf(data=SFE_polygon_ubersimple, colour = NA) +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) +
  theme(legend.position = c(0.72,0.2),
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        legend.key.width = unit(.2, "in"),
        legend.key.height = unit (.15, "in"),
        legend.direction = "horizontal",
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.background = element_rect(fill = "grey90", color = NA),
        panel.background = element_rect(fill = 'grey90')) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5)) +
  xlab("") +
  ylab("")
  
#STRBAS_sd

# Arrange plots side by side
STRBAS_slope_plot <- ggarrange(STRBAS_slope,STRBAS_sd,nrow = 1,ncol = 2,align = c("hv"))

# Save STRBAS plot component
ggsave("../Figures/042022/STRBAS_slope.png", plot = STRBAS_slope_plot, dpi = 500, width = 6.5, height = 4)
```

### Delta Smelt components - 3b

Figure of spatial slope value as well as standard deviation and overall estimate for Delta Smelt

```{r}
# Read in Delta Smelt predictions
pDELSME_2017 <- readRDS("../predictions/042022/pDELSME_ss.rds")

# Delta smelt slope
DELSME_slope <- pDELSME_2017 %>%
  ggplot() +
  geom_raster(aes(X*1000,Y*1000,fill=zeta_s)) +
  scale_fill_gradient2(
  low = "red",
  mid = "white",
  high = "blue",
  midpoint = 0,
  limits = c(-2,2),
  name = "Spatial Slope") +
  theme_classic2() +
  geom_sf(data=SFE_polygon_ubersimple, colour = NA) +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) +
  theme(legend.position = c(0.72,0.2),
        axis.text.y = element_text(size = 8),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.key.width = unit(.2, "in"),
        legend.key.height = unit (.15, "in"),
        legend.direction = "horizontal",
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.background = element_rect(fill = "grey90", color = NA),
        panel.background = element_rect(fill = 'grey90')) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5)) +
  xlab("") +
  ylab("")

#DELSME_slope

# Delta smelt slope standard deviation
DELSME_sd <- pDELSME_2017 %>%
  ggplot() +
  geom_raster(aes(X*1000,Y*1000,fill=sd)) +
  scale_fill_viridis_c(name = "Spatial Slope SD") +
  theme_classic2() +
  geom_sf(data=SFE_polygon_ubersimple, colour = NA) +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) +
  theme(legend.position = c(0.72,0.2),
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        legend.key.width = unit(.2, "in"),
        legend.key.height = unit (.15, "in"),
        legend.direction = "horizontal",
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.background = element_rect(fill = "grey90", color = NA),
        panel.background = element_rect(fill = 'grey90')) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5)) +
  xlab("") +
  ylab("")
  
#DELSME_sd

# Arrange plots side by side
DELSME_slope_plot <- ggarrange(DELSME_slope,DELSME_sd,nrow = 1,ncol = 2,align = c("hv"))

# Save DELSME plot component
ggsave("../Figures/042022/DELSME_slope.png", plot = DELSME_slope_plot, dpi = 500, width = 6.5, height = 4)
```

### Longfin Smelt Components - 3c

```{r}
# Read in Longfin Smelt predictions
pLONSME_2017 <- readRDS("../predictions/042022/pLONSME_ss.rds")

# Longfin Smelt slope
LONSME_slope <- pLONSME_2017 %>%
  ggplot() +
  geom_raster(aes(X*1000,Y*1000,fill=zeta_s)) +
  scale_fill_gradient2(
  low = "red",
  mid = "white",
  high = "blue",
  midpoint = 0,
  limits = c(-2,2),
  name = "Spatial Slope") +
  theme_classic2() +
  geom_sf(data=SFE_polygon_ubersimple, colour = NA) +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) +
  theme(legend.position = c(0.72,0.2),
        axis.text.y = element_text(size = 8),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.key.width = unit(.2, "in"),
        legend.key.height = unit (.15, "in"),
        legend.direction = "horizontal",
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.background = element_rect(fill = "grey90", color = NA),
        panel.background = element_rect(fill = 'grey90')) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5)) +
  xlab("") +
  ylab("")

#LONSME_slope

# Longfin Smelt slope standard deviation
LONSME_sd <- pLONSME_2017 %>%
  ggplot() +
  geom_raster(aes(X*1000,Y*1000,fill=sd)) +
  scale_fill_viridis_c(name = "Spatial Slope SD") +
  theme_classic2() +
  geom_sf(data=SFE_polygon_ubersimple, colour = NA) +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) +
  theme(legend.position = c(0.72,0.2),
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        legend.key.width = unit(.2, "in"),
        legend.key.height = unit (.15, "in"),
        legend.direction = "horizontal",
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.background = element_rect(fill = "grey90", color = NA),
        panel.background = element_rect(fill = 'grey90')) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5)) +
  xlab("") +
  ylab("")
  
#LONSME_sd

# Arrange plots side by side
LONSME_slope_plot <- ggarrange(LONSME_slope,LONSME_sd,nrow = 1,ncol = 2,align = c("hv"))

# Save LONSME plot component
ggsave("../Figures/042022/LONSME_slope.png", plot = LONSME_slope_plot, dpi = 500, width = 6.5, height = 4)
```

### Threadfin Shad Components - 3d

```{r}
# Read in Threadfin Shad predictions
pTHRSHA_2017 <- readRDS("../predictions/042022/pTHRSHA_ss.rds")

# Threadfin Shad slope
THRSHA_slope <- pTHRSHA_2017 %>%
  ggplot() +
  geom_raster(aes(X*1000,Y*1000,fill=zeta_s)) +
  scale_fill_gradient2(
  low = "red",
  mid = "white",
  high = "blue",
  midpoint = 0,
  limits = c(-2,2),
  name = "Spatial Slope") +
  theme_classic2() +
  geom_sf(data=SFE_polygon_ubersimple, colour = NA) +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) +
  theme(legend.position = c(0.72,0.2),
        axis.text.y = element_text(size = 8),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.key.width = unit(.2, "in"),
        legend.key.height = unit (.15, "in"),
        legend.direction = "horizontal",
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.background = element_rect(fill = "grey90", color = NA),
        panel.background = element_rect(fill = 'grey90')) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5)) +
  xlab("") +
  ylab("")

#THRSHA_slope

# Threadfin Shad slope standard deviation
THRSHA_sd <- pTHRSHA_2017 %>%
  ggplot() +
  geom_raster(aes(X*1000,Y*1000,fill=sd)) +
  scale_fill_viridis_c(name = "Spatial Slope SD") +
  theme_classic2() +
  geom_sf(data=SFE_polygon_ubersimple, colour = NA) +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) +
  theme(legend.position = c(0.72,0.2),
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        legend.key.width = unit(.2, "in"),
        legend.key.height = unit (.15, "in"),
        legend.direction = "horizontal",
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.background = element_rect(fill = "grey90", color = NA),
        panel.background = element_rect(fill = 'grey90')) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5)) +
  xlab("") +
  ylab("")
  
#THRSHA_sd

# Arrange plots side by side
THRSHA_slope_plot <- ggarrange(THRSHA_slope,THRSHA_sd,nrow = 1,ncol = 2,align = c("hv"))

# Save THRSHA plot component
ggsave("../Figures/042022/THRSHA_slope.png", plot = THRSHA_slope_plot, dpi = 500, width = 6.5, height = 4)
```

### American Shad Components - 3e

```{r}
# Read in American Shad predictions
pAMESHA_2017 <- readRDS("../predictions/042022/pAMESHA_ss.rds")

# American Shad slope
AMESHA_slope <- pAMESHA_2017 %>%
  ggplot() +
  geom_raster(aes(X*1000,Y*1000,fill=zeta_s)) +
  scale_fill_gradient2(
  low = "red",
  mid = "white",
  high = "blue",
  midpoint = 0,
  limits = c(-2,2),
  name = "Spatial Slope") +
  theme_classic2() +
  geom_sf(data=SFE_polygon_ubersimple, colour = NA) +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) +
  theme(legend.position = c(0.72,0.2),
        axis.text.y = element_text(size = 8),
        axis.text.x = element_text(size = 8, angle = 45, vjust = 0.5, hjust = 0.5),
        legend.key.width = unit(.2, "in"),
        legend.key.height = unit (.15, "in"),
        legend.direction = "horizontal",
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.background = element_rect(fill = "grey90", color = NA),
        panel.background = element_rect(fill = 'grey90')) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5)) +
  xlab("") +
  ylab("")

#AMESHA_slope

# American Shad slope standard deviation
AMESHA_sd <- pAMESHA_2017 %>%
  ggplot() +
  geom_raster(aes(X*1000,Y*1000,fill=sd)) +
  scale_fill_viridis_c(name = "Spatial Slope SD") +
  theme_classic2() +
  geom_sf(data=SFE_polygon_ubersimple, colour = NA) +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) +
  theme(legend.position = c(0.72,0.2),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 8, angle = 45, vjust = 0.5, hjust = 0.5),
        legend.key.width = unit(.2, "in"),
        legend.key.height = unit (.15, "in"),
        legend.direction = "horizontal",
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.background = element_rect(fill = "grey90", color = NA),
        panel.background = element_rect(fill = 'grey90')) +
  guides(fill = guide_colourbar(title.position="top", title.hjust = 0.5)) +
  xlab("") +
  ylab("")
  
#AMESHA_sd

# Arrange plots side by side
AMESHA_slope_plot <- ggarrange(AMESHA_slope,AMESHA_sd,nrow = 1,ncol = 2,align = c("hv"))

# Save AMESHA plot component
ggsave("../Figures/042022/AMESHA_slope.png", plot = AMESHA_slope_plot, dpi = 500, width = 6.5, height = 4)
```

# Figure 4

Plot of the overall trends in probability of detection at SFES survey points. Estimates are still in logit space so need to transform (plogis) for probability of detection.

```{r}
# Read in prediction grid
pred_all_species <- readRDS("../predictions/042022/pred_all_species.rds")

# Generate plot
overall_trend <- pred_all_species %>%
  ggplot(aes(x=Year,y=plogis(est),color=species,linetype=species)) +
  geom_smooth() +
  theme_bw() +
  ylab("Probability of Detection") +
  scale_color_discrete(labels = c("American Shad", "Delta Smelt", "Longfin Smelt", "Striped Bass", "Threadfin Shad"), name = "Species") +
  scale_linetype_discrete(labels = c("American Shad", "Delta Smelt", "Longfin Smelt", "Striped Bass", "Threadfin Shad"), name = "Species") +
  theme(legend.position = "top") #+
  coord_trans(y = "sqrt")

overall_trend

# Save plot
ggsave("../Figures/051622/overall_trend.png", plot = overall_trend, height = 7, width = 7, dpi = 600)
```

# Figure 5

### Center of gravity plots
Keep in mind these were generated using predictions on SFES survey points because computer could not handle predictions over the entire 500x500m grid.

```{r}
library(tidymv)

# Read in COG GAM fit and COG point/range estimates
mCOG <- readRDS("../COG/021523/mCOG.rds")
cog <- readRDS("../COG/021523/cog_fit.rds")

# Generate center of gravity plot with the 5 species estimates, estimate ranges, and fit with 95% CI

cog_plot <- ggplot(data = cog, aes(x=Year, y=fit)) + 
  geom_smooth_ci(species, show.legend = F) +
  geom_pointrange(data = cog, aes(x=Year,y=est,ymin=lwr,ymax=upr,color=species, shape = species), size = 0.5, fatten = 2) +
  theme_bw() +
  ylab("Center of Gravity - Easting (km)") +
  scale_color_discrete(name = "Species", labels = c("American Shad", "Delta Smelt", "Longfin Smelt", "Striped Bass", "Threadfin Shad")) +
  scale_shape_discrete(name = "Species", labels = c("American Shad", "Delta Smelt", "Longfin Smelt", "Striped Bass", "Threadfin Shad")) +
  theme(legend.position = "top") +
  xlab("Year") +
  scale_y_continuous(breaks = c(560,570,580,590,600,610))

cog_plot

# Generate COG plot of outflow spline

cog_of <- plot_smooths(mCOG, series = outflow_maf, comparison = species) +
  theme_bw() +
  ylab("Center of Gravity - Easting (km)") +
  xlab("Delta Outflow (maf)") +
  theme(legend.position = "bottom") +
  scale_linetype_discrete(name = "Species", 
                          labels = c("American Shad", "Delta Smelt", "Longfin Smelt", "Striped Bass", "Threadfin Shad")) +
  scale_color_discrete(name = "Species", labels = c("American Shad", "Delta Smelt", "Longfin Smelt", "Striped Bass", "Threadfin Shad")) +
  scale_fill_discrete(name = "Species", labels = c("American Shad", "Delta Smelt", "Longfin Smelt", "Striped Bass", "Threadfin Shad"))

cog_of

# Combine plots
cog_out <- ggarrange(cog_plot, cog_of, nrow = 2, ncol = 1)

cog_out

# Save figure
ggsave("../Figures/011223/COG_outflow.png", plot = cog_out, height = 6, width = 7.5)
```

# Table 2
Print model outputs

```{r}
library(sdmTMB)

# Read in models
mSTRBAS <- readRDS("../output_models/042022/mSTRBAS.rds")
mDELSME <- readRDS("../output_models/042022/mDELSME.rds")
mLONSME <- readRDS("../output_models/042022/mLONSME.rds")
mTHRSHA <- readRDS("../output_models/042022/mTHRSHA.rds")
mAMESHA <- readRDS("../output_models/042022/mAMESHA.rds")

# Print model results
summary(mSTRBAS)
summary(mDELSME)
summary(mLONSME)
summary(mTHRSHA)
summary(mAMESHA)
```

# Table 3

Print results of simple GAM showing effect of year, species, and outflow on COG

```{r}
summary(mCOG)
```

# Appendix Figure 1

```{r}
# Filter out just 2017 since stations are the same each year
SFES_2017 <- SFES %>%
  filter(Year == 2017) 

# Plot location of stations with color/shape by survey
SFES_stations <- ggplot() +
  geom_sf(data=SFE_polygon_ubersimple, colour = NA) +
  coord_sf(xlim = c(535403, 653022), ylim = c(4139322, 4240550), expand = FALSE) + 
  geom_point(data=SFES_2017,
             aes(X*1000,Y*1000,colour=Survey,shape=Survey), 
             width = 2, height = 2, 
             position = position_dodge(width = 1500)) + 
  scale_shape_manual(values=1:nlevels(SFES_2017$Survey), 
                     labels = c("Bay Study Midwater Trawl",
                                "Bay Study Otter Trawl",
                                "Beach Seine Survey",
                                "Chipps Island Trawl",
                                "Fall Midwater Trawl",
                                "Suisun Marsh Beach Seine",
                                "Suisun Marsh Otter Trawl",
                                "Summer Townet Survey")) +
  scale_color_discrete(labels = c("Bay Study Midwater Trawl",
                                "Bay Study Otter Trawl",
                                "Beach Seine Survey",
                                "Chipps Island Trawl",
                                "Fall Midwater Trawl",
                                "Suisun Marsh Beach Seine",
                                "Suisun Marsh Otter Trawl",
                                "Summer Townet Survey")) +
  theme_classic2() +
  xlab("Longitude") +
  ylab("Latitude") +
  theme(legend.position = "top")
  

# Save plot
ggsave("../Figures/051622/SFES_stations.png", SFES_stations, width = 9, height = 7)
```

### STN vs. BS catch at one site
This is in response to a reviewer's concern that the fish are moving to the fringes, away from the path of the trawls, making the decline look larger than it actually is. Sommer et al. (2011) showed this as well.

Sites near Terminous:
  BSS LP003E
  STN 919
  
Sites Near Rio Vista:
  BSS SR014W
  FMWT 710
  
Sites Suisun Marsh:
  SMOT CO2
  STN 606
  FMWT 606

```{r}
# Read in SFES data
SFES <- readRDS("../Input_data/SFES_111621.rds")

# Filter out STN and BSS site near Terminous
comp_sites <- SFES %>%
  filter(Survey %in% c("STN","BSS","SMOT","FMWT"),
         Station %in% c("LP003E","919","SR014W","710","CO2","606")) %>%
  select(Year,Survey,Station,STRBAS,DELSME,AMESHA,THRSHA,LONSME)

# Plot catch against one another
terminous <- comp_sites %>%
  filter(Station %in% c("LP003E","919")) %>%
  ggplot(aes(x=Year,y=DELSME,color=Survey)) +
  geom_smooth() +
  ggtitle("Terminous Stations") +
  ylab("Delta Smelt Catch") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

rio_vista <- comp_sites %>%
  filter(Station %in% c("SR014W","710")) %>%
  ggplot(aes(x=Year,y=DELSME,color=Survey)) +
  geom_smooth() +
  ggtitle("Rio Vista Stations") +
  ylab("Delta Smelt Catch") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

suisun_marsh <- comp_sites %>%
  filter(Station %in% c("CO2","606")) %>%
  ggplot(aes(x=Year,y=STRBAS,color=Survey)) +
  geom_smooth() +
  ggtitle("Suisun Marsh Stations") +
  ylab("Striped Bass Catch") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

# Arrange Plots Together
ggarrange(terminous,rio_vista,suisun_marsh, align = "hv")

# Save plot
ggsave("../Figures/011223/Appendix_F2.png",dpi=600,width=7.5,height=6)
```

  